Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-15 WSSSPE3/report/wg_main_best_practices.tex
added missing periods

\subsubsection{Landing Page}
The landing page with instructions, timeline and the white paper is here: \url{https://drive.google.com/drive/folders/0B7KZv1TRi06fbnFkZjQ0ZEJKckk}
Discussions can be also continued in \url{https://github.com/WSSSPE/meetings/issues/42}

>>>>

\subsubsection{Landing Page}
The landing page with instructions, timeline and the white paper is here: \url{https://drive.google.com/drive/folders/0B7KZv1TRi06fbnFkZjQ0ZEJKckk}.
Discussions can be also continued in \url{https://github.com/WSSSPE/meetings/issues/42}.
